%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Formal Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Certificate in Spanish Language Pedagogics} % Degree
    {Instytut Cervantesa w Krakowie} % Institution
    {Poland, Kraków} % Location
    {Sept. 2015 - Dec. 2015} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Learnt about the theory behind Public Speech, Group Dynamics, and Skills Learning.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Studies in Pure and Abstract Mathematics} % Degree
    {Universidad Complutense de Madrid} % Institution
    {Madrid, Spain} % Location
    {Sept. 2010 - Jan. 2015} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Honour Grade in General Topology. Mentions of Excellence in Algebra, Geometry and Set Theory.}
            \item {The habits of the mathematician: it's not true until you prove it, there-is-always-a-better-way way of thinking, and taste for abstractions.}
            \item {Interests in classification problems and pattern laws.}
        \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Sciences Baccalaurate} % Degree
    {I.E.S. Luis de Lucena} % Institution
    {Guadalajara, Spain} % Location
    {Sept. 2008 - May. 2010} % Date(s)
    {
        \begin{cvitems} % Description(s) bullet points
            \item {Performant in Philosophy, Physics, Mathematics and Biology.}
            \item {Time has shown me that high-school was a lot more valuable than I thought back then. To this day, I don't see a red moon in the horizon, I see a refracted electromagnetic field stimulating cone cells which release a chain of sodium-potassium reaction along a neural axon.}
        \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
