%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry{Software Developer} % Job title
    {Motorola Solutions Poland} % Organization
    {Kraków, Poland} % Location
    {June 2018 --- PRESENT} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I am The Git Master of the team. I am responsible for directing the branching model,
                reviewing and merging pull requests, managing the build system, and keeping my team
            trained and up-to-date.}
        \item {Accomplished an upgrade of the toolchains and code of a legacy product: upgraded to
                the latest Visual C++ (v141) compiler and latest {.NET} (4.7.2), and fixed and
            improved the mixed libraries, dealing with the Garbage Collector and kernel mapped memory.}
        \item {Maintenance and refactoring of critical-mission telecommunications software,
                promoting static analysis, strong typing, polymorphism, separation of concerns,
            generic programming and good design patterns.}
        \item {Development of the CD \& CI platforms: whole integration of Jenkins, git, NAnt,
            Jira, BitBucket, and Artifactory.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{Automation Process Developer} % Job title
    {IBM BTO Services Poland} % Organization
    {Kraków, Poland} % Location
    {Nov. 2017 --- May 2018} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reassessment of the team practices and quality standards.}
            \begin{itemize}
                \item {Exposed ERP APIs by C++/COM compliant binaries for automation purposes,
                    so other developers could take advantage from different languages and frameworks.}
                \item {Implemented C++ Command-Line applications using cutting-edge toolchains
                    (Visual C++ 17, GCC 6.4) as a wrapper around Citrix and other streaming services
                for a more stable, deterministic and easy to use networks.}
                \item {Developed code standards, promoted design patterns and a Test-Driven Design approach.}
            \end{itemize}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{Accountant Automation} % Job title
    {IBM BTO Services Poland} % Organization
    {Kraków, Poland} % Location
    {Feb. 2017 --- Oct. 2017} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development of automation tools for the finance sector. Scripting and Automation
                tools using Visual Basic, Powershell and Python, to improve efficiency of the
            reporting processes.}
        \item {Responsible for the Accounts Payable department of the client's Spanish section.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
