%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry{Motorola Solutions Poland} % Company
    {Malloc Alone} % Event
    {Kraków, Poland} % Location
    {January 2018} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {Following a parallel story to that of the famous movie `Home Alone', I told the story
                of little Malloc, who ought to be responsible for the whole management of memory. Four
                main ideas in display: Virtual Memory, Allocators, Garbage Collectors, and Ownership
            Semantics.}
        \item {Introduced Virtual Memory from the perspective of the kernel.}
        \item {Showed how a classic allocator works, and how we can implement our own custom
            allocators.}
        \item {Explained the theory of Garbage Collection, showing examples of native code
            interfacing GCs going wrong and possible solutions.}
        \item {Promoted RAII and Ownership Semantics as a zero-cost abstraction, backed by
            mathematical theories like Linear Logic.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{Motorola Solutions Poland} % Company
    {Know your Computers, a History} % Event
    {Kraków, Poland} % Location
    {December 2018} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {A crash course history of computers, starting from Hilbert's Millennia Problems, among
                which the Entscheidunsproblem, or decision problem, better known from its
            corolary, the Halting Problem.}
        \item {Turing's Almigthy Universal Machine as solution to the Halting problem. Von Neumann's
                Architecture as a Turing Machine made real, and Fortran as a first high-level
            language, followed by Backus' infamous Turing Award talk and Hoare's regrets.}
        \item {Meltdown, Spectre, and the relationships between the evolution of hardware and the
                evolution of programming languages, and how they have had to evolve together.
                Presented features of modern hardware like Branch Prediction, cache lines,
                out-of-order execution, SIMD, Transactional Memory, together with advise and
            examples on how to take advantage of them.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{Motorola Solutions Poland} % Company
    {Everything you ever wanted to know about git} % Event
    {Kraków, Poland} % Location
    {September 2018} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {The beauty of a \textit{Dyrected Acyclic Graph} and how it saves history safely as a
            Merkle tree.}
        \item {Git under the hood: commits, blobs, hashing, and what does all of that mean for merging.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{IBM BTO Services Polska} % Company
    {Hooking Dlls for extra functionality} % Event
    {Kraków, Poland} % Location
    {March 2018} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {Exposed a C++ application around networking binaries (Citrix, VMware) to take
            advantage of undocumented functionality.}
        \item {Methodically presented my ongoing R\&D on this topic for further investment on the
            improvement of the company's models.}
        \end{cvitems}
    }

    %---------------------------------------------------------
    \cventry{IBM BTO Services Polska} % Company
    {Interfacing to new Libraries} % Event
    {Kraków, Poland} % Location
    {February 2018} % Date(s)
    {
        \begin{cvitems} % Description(s)
        \item {Developed a series of COM libraries to take advantage of, in the automation of ERP
            systems and local databases.}
        \item {Presented it to my team, in an pedagogic and entertaining fashion, influencing the
            of ERP sysany development's policies.}
        \end{cvitems}
    }

    %---------------------------------------------------------
\end{cventries}
